\documentclass[letterpaper,11pt]{article}

\usepackage{titlesec} % for \titleformat command
\usepackage[usenames,dvipsnames]{color} % for \color command
\usepackage{enumitem} %for [leftmargin=*] in \resumeSubHeadingListStart itemize environment 
\usepackage[empty]{fullpage} %sets margins to fullpage 
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref} % For website urls 
\usepackage{style_cv} % My stylesheet based on MIT/ Sourabh Bajaj
\usepackage[left=0.5cm, right=0.5cm, top=1cm, bottom=0.5cm]{geometry} %Set margins
\pdfgentounicode=1
\urlstyle{same}
\setlength{\footskip}{4.09pt}

\begin{document}

%----------HEADING-----------------
\begin{center}
{\huge \textbf{William Spagnola}} 
\end{center}
\vspace{-10pt}
\small

% Note: Should Figure out how to center center column properly without using \hspace
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r}

	470 Lenox Ave. & 
	\hspace{24pt}\href{https://www.williamspagnola.com/}{williamspagnola.com}  & 
	717-683-4039 \\ 
	
	New York, NY 10037  &
	\hspace{24pt}\href{https://github.com/wspagnola/}{github.com/wspagnola}  &
	\href{mailto:william.spagnola@nyu.edu}{william.spagnola@nyu.edu}  \\
	
\end{tabular*}


\vspace{-12pt}
%%-----------EXPERIENCE-----------------
\section{Experience}
	\resumeSubHeadingListStart
	
		\resumeSubheading
			{Research Alliance for New York City Schools}{New York, NY}
			{Technical Research Analyst}{July 2019 to present}
			\resumeItemListStart
				\resumeItem{Maintain data pipeline and design data structures in preparation for analysis using SQL and SAS. }
				\resumeItem{Designed regression discontinuity study to analyze causal effect of Career and Technical Education on high school graduation.}  
				\resumeItem {Created Logistic Regression model to predict dropout risk among New York City public high school students.} 
				\resumeItem{Developed survey questions to measure effect of after-school program for disadvantaged students on STEM awareness.  Planned logistics of obtaining consent and distributing the survey via Qualtrics.}
			\resumeItemListEnd
			
		\resumeSubheading
			{Tobacco Research Lab} {New York, NY}
			{Research Intern}{January 2019 to June 2019}
			\resumeItemListStart
				\resumeItem{Estimated probability of smoking initiation,  cessation, and relapse over time from longitudinal survey data.  Presented results in interactive visualization to illustrate changes in tobacco use.  }
			\resumeItemListEnd

	\resumeSubheading
	{The Rusk Institute of Rehabilitation Medicine} {New York, NY}
	{Statistical Consultant}{February 2018 to June 2019}
		\resumeItemListStart
			\resumeItem{Consulted on study of correlations between cytokine types and fibromyalgia.   Provided advice on non-parametric methods and  multiple comparisons adjustments.   Article published in \textit{The Journal of the International Association for the Study of Pain}.}
			\resumeItem {Collaborated on study proposal of the effects of Heart Rate Variability using simulation and multi-level modeling.}
			\resumeItem {Provided statistical consulting for research on the effectiveness of exercise and speech therapy.}
		\resumeItemListEnd
	
	\resumeSubheading
	{New York City Department of Education}{Bronx, NY}
	{Special Education Teacher}{September 2009 to June 2016}
		\resumeItemListStart
			\resumeItem {Taught students with autism and intellectual disabilities in a public special education high school.}
		\resumeItemListEnd
	\resumeSubHeadingListEnd
%-----------EDUCATION-----------------

\section{Education}
	\resumeSubHeadingListStart
   		\resumeSubheadingAward
      		{New York University}{New York, NY}
      		{Master of Science in Applied Statistics for Social Science Research;  GPA: 4.00}{}
      		{Recipient of Western Scholarship}{}
      	\resumeSubheading
      		{Pace University}{New York, NY}
      		{Master of Science in Special Education} {}
      	\resumeSubheading
      		{Loyola University}{Baltimore, MD}
      		{B.A. in English Literature with Spanish Minor}{}
    \resumeSubHeadingListEnd

%------------- PROJECTS ------------------
\section{Projects}
\resumeItemListStart

	\projectItem {Advent of Code}
				{Completed daily coding challenges using NumPy and Pandas.}
	\projectItem {Machine Learning Project on 2016 Election Data}
				 {Identified clusters in county-level presidential data using k-means and model-based clustering algorithms.}
	\projectItem {Interactive Shiny App for COVID19 Data}
				 {Created interactive/up-to-date dashboard of COVID case and death data at country,  state,  and county levels.}
	\projectItem{Gender Dynamics in Data Science Survey Project}
				{Collaborated on a team to create a survey to investigate perceptions of gender and ability in data science.}
	\projectItem {NYPD Crime Data Visualization}
				 {Won award from NYU Statistics Club for creating data visualization that compared New York City crime rates on Halloween to yearly averages.}
	\projectItem{Family Heritage Website}
				{Developed website on Pennsylvanian German family history for genealogy organization.}
\resumeItemListEnd


% Updated process Missing Data using Fully conditional specification/stochastic regresison model 

% Designed SAS macros: 
%% 1) Display regression discontinuity using binned scatter plots
%% 2) Identify cutoffs in R discontinuities
%% 3) Estimated causal effects using local linear probability model with fixed effects
%% 4) Create SAS function for RCT/RDD Anaylsis 
			%%% Add covariates
			%%% Add fixed effects
			%%% Add cluster standard errors
			%%% Add multiple outcome variables and output table with impact estimates 

% ES Options
%% Google Apps Script: Mail merge and send consent/assent forms
%% Qualtrics to distrubte survey students 
%% Helped designed multi-level study for WWC; Preliminarily receive 
%% Used PCA to find clusters of questions[?]
%% Use Cronbach's Alpha to asses internal consistencies of constructs.

%	\projectItem {NYPD Stop and Frisk Data}
%				{Designed logistic regression model to investigate police data based on police stops and predict probability of finding weapons }

%Skills: Stata,  Emacs,  Vim,  Linux,  Latex



% Machine Learning Project to Predict NYC High School Graduation Rates: Created models using Random
%Forest and Lasso Regression to predict school-level graduation rates based on data obtained from the New York City Department of Education.
% Causal Inference: Simulated data to study how violations of assumptions affected treatment estimates in Regression
% Reproducibility Study on Airbnb: Researched racial discrimination in the online rental market by replicating th results from a study on Airbnb and using multiple linear regression to perform original analyses on the interaction ffects %of race with other variables.
% Tableau Dashboard: Election Data 
% Causal Inference: Simulated data to study how violations of assumptions affected treatment estimates in Regression Discontinuity, Instrumental Variable, and Fixed-Effects Panel Data designs
% Unsupervised Learning Project on 2016 Election Data: Investigated county-level presidential election trends using k-means and model-based clustering algorithms.
% Webscraping/Text Analysis: Beatles Chords  
% Twitter/NLP Project:  Tweets Naive Bayes; Trump or Staff



% ------------- SKILLS	------------------

\section{Skills}
\vspace{-1pt}
\begin{itemize}
\small
\begin{minipage}{0.3\linewidth}
    \item R and RShiny
    \item Python
    \item SQL
\end{minipage}
% Note you have to add as many items here as are in the two columns
\begin{minipage}{0.025\linewidth}
	\item[\hspace{\fill}]
	\item[\hspace{\fill}]
	\item[\hspace{\fill}]
\end{minipage}
\begin{minipage}{0.3\linewidth}
    \item Tableau
    \item Stata
    \item SQL
\end{minipage}
\begin{minipage}{0.025\linewidth}
	\item[\hspace{\fill}]
	\item[\hspace{\fill}]
	\item[\hspace{\fill}]
\end{minipage}
\begin{minipage}{0.3\linewidth}
	\item Google Apps Script
    \item Git
    \item HTML/CSS
\end{minipage}
\end{itemize}

\end{document}


